Lesson 3
========================================================

***

### What to Do First?
Notes:setwd()

***

### Pseudo-Facebook User Data
Notes:

```{r Pseudo-Facebook User Data}
setwd('d:/Excellent/python/da-advance/lesson23')
list.files()
pf<-read.csv('pseudo_facebook.tsv',sep='\t')

```

***

### Histogram of Users' Birthdays
Notes:

```{r Histogram of Users\' Birthdays}
install.packages('ggplot2')
library(ggplot2)
install.packages('ggthemes',dependencies = TRUE)
library(ggthemes) 
theme_set(theme_minimal(24)) 
names(pf)
qplot(x = dob_day,data=pf,bins=31)+
  scale_x_continuous(breaks = 1:50)

```

***

#### What are some things that you notice about this histogram?
Response:

***

### Moira's Investigation
Notes:
***

### Estimating Your Audience Size
Notes:

***

#### Think about a time when you posted a specific message or shared a photo on Facebook. What was it?
Response:

#### How many of your friends do you think saw that post?
Response:
10
#### Think about what percent of your friends on Facebook see any posts or comments that you make in a month. What percent do you think that is?
Response:
60%
***

### Perceived Audience Size
Notes:

***
### Faceting
Notes:

```{r Faceting}
qplot(x = dob_day,data=pf)+
  scale_x_continuous(breaks = 1:31)+
  facet_wrap(~dob_month,ncol=3)

```

#### Letâs take another look at our plot. What stands out to you here?
Response:
1月1日最多
***

### Be Skeptical - Outliers and Anomalies
Notes:
警惕异常值
***

### Moira's Outlier
Notes:
#### Which case do you think applies to Moiraâs outlier?
Response:
排除极端值的坏数据
***

### Friend Count
Notes:

#### What code would you enter to create a histogram of friend counts?

```{r Friend Count}
qplot(x=friend_count,data=pf)

```

#### How is this plot similar to Moira's first plot?
Response:
细致很多更清晰
***

### Limiting the Axes
Notes:

```{r Limiting the Axes}
qplot(x=friend_count,data=pf,xlim=c(0,1000))

qplot(x=friend_count,data=pf)+
  scale_x_continuous(limits=c(0,1000))

```

### Exploring with Bin Width
Notes:
调整组距

***

### Adjusting the Bin Width
Notes:

### Faceting Friend Count
```{r Faceting Friend Count}
# What code would you add to create a facet the histogram by gender?
# Add it to the code below.
qplot(x = friend_count, data = pf, binwidth = 10) +
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50))+
  facet_wrap(~gender)
```

***

### Omitting NA Values
Notes:忽略掉NA的

```{r Omitting NA Values}
qplot(x = friend_count, data = subset(pf,!is.na(gender)), binwidth = 10) +
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50))+
  facet_wrap(~gender)

qplot(x = friend_count, data = na.omit(pf), binwidth = 10) +
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50))+
  facet_wrap(~gender)

```

***

### Statistics 'by' Gender
Notes:

```{r Statistics \'by\' Gender}
table(pf$gender)
by(pf$friend_count,pf$gender,summary)


```

#### Who on average has more friends: men or women?
Response:
women

#### What's the difference between the median friend count for women and men?
Response:
22

#### Why would the median be a better measure than the mean?
Response:
更普遍的反映真实的情况

***

### Tenure
Notes:

```{r Tenure}
qplot(x=tenure,data=pf,binwidth=30,color=I('black'),fill=I('#099DD9'))



```

***

#### How would you create a histogram of tenure by year?

```{r Tenure Histogram by Year}
qplot(x=tenure/365,data=pf,binwidth=0.25,color=I('black'),fill=I('#F79420'))+
  scale_x_continuous(breaks = seq(1,7,1),limits=c(0,7))
```

***

### Labeling Plots
Notes:

```{r Labeling Plots}
qplot(x=tenure/365,data=pf,xlab='Number of years using Facebook',ylab = 'Number of users in sample',binwidth=0.25,color=I('black'),fill=I('#F79420'))+
  scale_x_continuous(breaks = seq(1,7,1),limits=c(0,7))

```

***

### User Ages
Notes:

```{r User Ages}
summary(pf$age)
qplot(x=age,data=pf,xlab='Number of years using Facebook',ylab = 'Number of users in sample',binwidth=5,color=I('black'),fill=I('#F79420'))+
  scale_x_continuous(breaks = seq(1,113,5),limits=c(0,113))

```

#### What do you notice?
Response:
还有其他可以修改
***

### The Spread of Memes
Notes:

***

### Lada's Money Bag Meme
Notes:

***

### Transforming Data
Notes:
通过取2的对数10的对数,以及开方的方式来转换
***

### Add a Scaling Layer
Notes:

```{r Add a Scaling Layer}
summary(pf$friend_count)
summary(log10(pf$friend_count+1))
summary(sqrt(pf$friend_count))
install.packages('gridExtra') 
library(gridExtra)


p1<-qplot(x=friend_count,data=pf)
#p2<-qplot(x=log10(pf$friend_count+1),data=pf)
#p3<-qplot(x=sqrt(pf$friend_count),data=pf)

p2<-p1+scale_x_log10()
p3<-p1+scale_x_sqrt()


grid.arrange(p1,p2,p3,ncol=3)



```

***


### Frequency Polygons

```{r Frequency Polygons}
qplot(x = friend_count,y=..count../sum(..count..), data = subset(pf,!is.na(gender)), binwidth = 10,geom = 'freqpoly',color=gender) +
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50))

```

***

### Likes on the Web
Notes:

```{r Likes on the Web}
names(pf)
qplot(x = www_likes, data = subset(pf,!is.na(gender)),geom = 'freqpoly',color=gender)+
  scale_x_continuous()+
  scale_x_log10()
by(pf$www_likes,pf$gender,sum)

```


***

### Box Plots
Notes:

```{r Box Plots}
qplot(x = gender,y=friend_count, data = subset(pf,!is.na(gender)), geom='boxplot',ylim = c(0,1000))

qplot(x = gender,y=friend_count, data = subset(pf,!is.na(gender)), geom='boxplot')+
  scale_y_continuous(limits = c(0,1000))

qplot(x = gender,y=friend_count, data = subset(pf,!is.na(gender)), geom='boxplot')+
  coord_cartesian(ylim=c(0,1000))

```

#### Adjust the code to focus on users who have friend counts between 0 and 1000.

```{r}
qplot(x = gender,y=friend_count, data = subset(pf,!is.na(gender)), geom='boxplot')+
  coord_cartesian(ylim=c(0,250))

by(pf$friend_count,pf$gender,summary)

```

***

### Box Plots, Quartiles, and Friendships
Notes:

```{r Box Plots, Quartiles, and Friendships}

```

#### On average, who initiated more friendships in our sample: men or women?
Response:
#### Write about some ways that you can verify your answer.
Response:
```{r Friend Requests by Gender}
names(pf)
qplot(x=gender,y=friendships_initiated,data=subset(pf,!is.na(gender)),geom = 'boxplot')+
  coord_cartesian(ylim=c(0,1000))

```

Response:

***

### Getting Logical
Notes:

```{r Getting Logical}
summary(pf$mobile_likes)


summary(pf$mobile_likes>0)



pf$mobile_check_in<-ifelse(pf$mobile_likes>0,1,0)
pf$mobile_check_in<-factor(pf$mobile_check_in)
summary(pf$mobile_check_in)

sum(pf$mobile_check_in==1)/length(pf$mobile_check_in)

```

Response:

***

### Analyzing One Variable
Reflection:
单一变量的各种表示和计算
***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!