Lesson 5
========================================================

### Multivariate Data
Notes:

***

### Moira Perceived Audience Size Colored by Age
Notes:

***

### Third Qualitative Variable
Notes:

```{r Third Qualitative Variable}
library(ggplot2)
pf<-read.csv("D:/Excellent/python/da-advance/R-lesson/pseudo_facebook.tsv",sep="\t")
library(dplyr)

pf.fc_by_age_gender <- pf %>%
  filter(!is.na(gender)) %>%
  group_by(age,gender) %>%
  summarise( mean_friend_count = mean(friend_count),
             median_friend_count = median(friend_count),
             n = n()) %>%
  ungroup() %>%
  arrange(age)
head(pf.fc_by_age_gender)


ggplot(aes(x = gender, y = age),
       data = subset(pf, !is.na(gender))) + geom_boxplot()+stat_summary(fun.y=mean,geom='point',shape=4)

names(pf)

ggplot(aes(x=age,y=friend_count),data=subset(pf,!is.na(gender)))+geom_line(aes(color=gender),stat='summary',fun.y=median)

ggplot(aes(x = age, y = friend_count), 
  data = subset(pf, !is.na(gender))) +geom_line(aes(color = gender), stat = 'summary', fun.y = median)



```

***

### Plotting Conditional Summaries
Notes:

```{r Plotting Conditional Summaries}
names(pf.fc_by_age_gender)
ggplot(aes(x=age,y=median_friend_count),data=pf.fc_by_age_gender)+
  geom_line(aes(color = gender))
```
???????????????????????????????????????
***

### Thinking in Ratios
Notes:

***

### Wide and Long Format
Notes:

***

### Reshaping Data
Notes:

```{r}
install.packages('reshape2')
library(reshape2)

pf.fc_by_age_gender.wide<-dcast(pf.fc_by_age_gender,age ~ gender, value.var='median_friend_count')
head(pf.fc_by_age_gender)
head(pf.fc_by_age_gender.wide)
```


***

### Ratio Plot
Notes:

```{r Ratio Plot}
ggplot(aes(x=age,y=female/male),data=pf.fc_by_age_gender.wide)+geom_line()+geom_hline(yintercept=1,alpha=0.3,linetype=2)
```

***

### Third Quantitative Variable
Notes:

```{r Third Quantitative Variable}
pf$year_joined<-with(pf,floor(2014-tenure/365))
View(pf)
```

***

### Cut a Variable
Notes:

```{r Cut a Variable}
summary(pf$year_joined)
table(pf$year_joined)

pf$year_joined.bucket<-cut(pf$year_joined,c(2004,2009,2011,2012,2014))
View(pf$year_joined.bucket)
?cut
```

***

### Plotting it All Together
Notes:

```{r Plotting it All Together}
table(pf$year_joined.bucket,useNA = 'ifany')

ggplot(aes(x = age, y = friend_count), 
              data = subset(pf, !is.na(gender))) + 
  geom_line(aes(color = gender), stat = 'summary', fun.y = median)

ggplot(aes(x = age, y = friend_count), 
              data = subset(pf, !is.na(pf$year_joined.bucket))) + 
  geom_line(aes(color =year_joined.bucket ), stat = 'summary', fun.y = median)
```

***

### Plot the Grand Mean
Notes:

```{r Plot the Grand Mean}
ggplot(aes(x = age, y = friend_count), 
              data = subset(pf, !is.na(pf$year_joined.bucket))) + 
  geom_line(aes(color =year_joined.bucket ), stat = 'summary', fun.y = mean)+geom_line(stat='summary',fun.y=mean,linetype=2)
```

***

### Friending Rate
Notes:

```{r Friending Rate}
with(subset(pf,tenure>=1),summary(friend_count/tenure))
```

***

### Friendships Initiated
Notes:

What is the median friend rate?
0.22
What is the maximum friend rate?
417
```{r Friendships Initiated}

```

***

### Bias-Variance Tradeoff Revisited
Notes:

```{r Bias-Variance Tradeoff Revisited}

ggplot(aes(x = tenure, y = friendships_initiated / tenure),
       data = subset(pf, tenure >= 1)) +
  geom_line(aes(color = year_joined.bucket),
            stat = 'summary',
            fun.y = mean)

ggplot(aes(x = 7 * round(tenure / 7), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 30 * round(tenure / 30), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 90 * round(tenure / 90), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x=tenure,y=friendships_initiated / tenure),data=subset(pf,tenure>=1))+geom_smooth(aes(color=year_joined.bucket))

```

***

### Sean's NFL Fan Sentiment Study
Notes:

***

### Introducing the Yogurt Data Set
Notes:

***

### Histograms Revisited
Notes:

```{r Histograms Revisited}
yo<-read.csv('D:/Excellent/python/da-advance/R-lesson/yogurt.csv')
str(yo)
yo$id<-factor(yo$id)
ggplot(aes(x=price),data=yo)+geom_histogram(binwidth = 10)
```

***

### Number of Purchases
Notes:

```{r Number of Purchases}
length(unique(yo$price))
table(yo$price)
View(yo)
summary(yo)
yo<-transform(yo,all.purchases=strawberry+blueberry+pina.colada+plain+mixed.berry)
summary(yo$all.purchases)
```

***

### Prices over Time
Notes:

```{r Prices over Time}
names(yo)
ggplot(aes(x=time,y=price),data=yo)+geom_jitter(alpha=1/4,shape=21)
```

***

### Sampling Observations
Notes:

***

### Looking at Samples of Households

```{r Looking at Sample of Households}
set.seed(4230)
sample.ids<-sample(levels(yo$id),16)

ggplot(aes(x=time,y=price),data=subset(yo,id %in% sample.ids))+facet_wrap(~ id)+geom_line()+geom_point(aes(size=all.purchases),pch=1)
```

***

### The Limits of Cross Sectional Data
Notes:

***

### Many Variables
Notes:

***

### Scatterplot Matrix
Notes:

```{r}
install.packages('GGally')
library(GGally)
set.seed(1836)
pf_subset<-pf[,c(2:15)]
names(pf_subset)
ggpairs(pf_subset[sample.int(nrow(pf_subset),1000),])
```
***

### Even More Variables
Notes:

***

### Heat Maps
Notes:

```{r}
nci <- read.table("D:/Excellent/python/da-advance/R-lesson/nci.tsv")
colnames(nci) <- c(1:64)
```

```{r}
library(reshape2)
nci.long.samp <- melt(as.matrix(nci[1:200,]))
names(nci.long.samp) <- c("gene", "case", "value")
head(nci.long.samp)

ggplot(aes(y = gene, x = case, fill = value),
  data = nci.long.samp) +
  geom_tile() +
  scale_fill_gradientn(colours = colorRampPalette(c("blue", "red"))(100))
```


***

### Analyzing Three of More Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

